The cut operation on matrix factorisations

### 2017-07-23 referee-reply.tex

\item p.10 added a more precise reference

\item p.11 the nonstandard notation has been fixed.

\item p.13 Added $F = k^n$.

\item p.14 added a definition for $\cat{M}$.

\item Typos in the penultimate sentence of the proof of Lemma 2.27 (now Lemma 2.28) corrected.

\item Extra line in the proof of Lemma 3.2 fixed.

\item Clarified the matrix assigned to $1 \in k$ in Remark 3.3.

\item In (3.5) explained the notation for K\"ahler differentials

\item Corrected ``this odd''

\item In Lemma 3.9 clarified which differential is being referred to.

\item Removed the reference to linear factorisation (it is not necessary).

\item Fixed the definition of a morphism of strong deformation retracts.

\item Changed one of the two $A$s to a $C$, near (4.9).

\item Fixed equality that should have been $\simeq$ in second sentence of Section $4.2$.

\item Proof of Lemma 4.16, changed ``commute'' to ``anticommute''.

\item Removed Remark 4.30.

\item Fixed typo in Definition 4.39.

\item End of p.44 added reference to definition of $\cat{C}_A$.

\item Fixed the definition of $T$ in Appendix B, and the typo in (B.7).

\item Fixed references.

@@

\end{enumerate}

In addition I have made some minor typographical corrections, and made the following more serious corrections:

\begin{enumerate}
\item I actually need the base ring $k$ to be noetherian in order for some completions to be flat algebras (see the footnote to the first sentence of the Background section), but this wasn't being assumed in the original version. 
\item In the original I took a completion from $k[y]$ to $k\llbracket y \rrbracket$ in order to ensure the existence of a connection (p.17 of the original). However what is actually needed is that this completion is separated and complete for the adic topology determined by the ideal $I$ generated by the partial derivatives $\partial_{y_i} V$, which is not true unless the origin is the only critical point. This was therefore a genuine error in the paper. However it is easily fixed by changing the completion to the $I$-adic completion everywhere, which has been done (see Definition 3.5).
\end{enumerate}

### 2017-07-23 cutsystems-new.tex
Re-submission version

Our primary motivation for introducing $\cat{C}$ is that it can be enriched over affine schemes; this is not true directly of $\LG_k$, because the composition is infinitary. For context we include a sketch, assuming $k$ is an algebraically closed field of characteristic zero. Given potentials $W(x), V(y)$, a matrix factorisation of $V(y) - W(x)$ is after choosing a homogeneous basis just a matrix
\be\label{eq:intro_capitalD}
D \in M_{2r}( k[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (V(y) - W(x)) \cdot I_{2r}
\ee
where we require that, dividing $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices. If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise matrix factorisations by the $k$-points of an affine scheme whose coordinates are the coefficients of the various monomials in each row and column of $D$.

We may add further coordinates and equations to encode closed odd operators satisfying Clifford relations \eqref{eq:clifford_relations_intro} and, in this way, for a choice of parameters $\lambda = (r, k, \ldots)$ define a scheme $\mathscr{M}_{\lambda}(W,V)$ such that as sets
\begin{equation}\label{eq:param_frmf}
\cat{C}(W,V) = \bigcup_{\lambda} \mathscr{M}_{\lambda}(W,V)_{k}
\end{equation}
where $Z_{k}$ denotes the $k$-points of a scheme $Z$. The cut operation is a polynomial function of its inputs, so there is an indexed family of morphisms of schemes
\be\label{eq:enrichment_morphisms_intro}
\mathscr{M}_\mu(V,U) \times \mathscr{M}_\lambda(W,V) \lto \mathscr{M}_{f(\lambda, \mu)}(W, U)
\ee
lifting the functor \eqref{eq:cut_functor_intro} on the level of objects for some function $f(\lambda, \mu)$ of indices. Finally, using the approach of Section \ref{example:computing_homs}, we can define for each pair of potentials $W,V$ and tuple of parameters $\lambda$ a bundle of Clifford representations
\be\label{eq:enrichment_intro_bundles}
\xymatrix{
\mathscr{H}\! om_{W,V,\lambda} \ar[d]\\
\mathscr{M}_\lambda(W,V) \times \mathscr{M}_\lambda(W,V)\,.
}
\ee
Given two finite-rank matrix factorisations $X,X'$ of $V - W$ the fiber of this vector bundle over the point $(X',X)$ is the Clifford representation $(X')^{\vee} \l X$ of \eqref{eq:final_finite_model_hom}, which is isomorphic to the Hom-complex $\Hom_{k[x,y]}(X',X)$ tensored with a suitable spinor representation. The enrichment of $\cat{C}$ consists of the family of schemes $\mathscr{M}_\lambda(W,V)$, the composition morphisms \eqref{eq:enrichment_morphisms_intro}, the bundles \eqref{eq:enrichment_intro_bundles}, and various other data satisfying natural constraints which encode the structure of the bicategory.

@@

\begin{example} Supercategories, superfunctors and supernatural transformations form a superbicategory $\Cat^{\operatorname{sup}}_k$.
\end{example}

@@

\begin{lemma}\label{lemma:whackamole} Let $X$ be a $C_n$-module in $\cat{T}$. The idempotent $e_n: X \lto X$ splits, say 
\[
\xymatrix@C+2pc{
X \ar@<1ex>[r]^-{f_0} & V \ar@<1ex>[l]^-{g_0}
}
\]
with $f_0 g_0 = 1_V$ and $g_0 f_0 = e_n$ and in $\cat{T}^\bullet$ there are mutually inverse isomorphisms
\[
\xymatrix@C+2pc{
(X, n) \ar@<1ex>[r]^-{f} & (V,0) \ar@<1ex>[l]^-{g}\,.
}
\]
induced by $f_0,g_0$. In particular
\be
S_n^* \otimes_{C_n} X \cong V\,, \qquad S_n \otimes_k V \cong X\,.
\ee
\end{lemma}
\begin{proof}
The map $f_0$ is a morphism $(X,n) \lto (V,0)$ in $\cat{T}^{\star}$ since
\[
f_0 \fermc_i = f_0 e_n \fermc_i = f_0 \ferm_1 \cdots \ferm_n \fermc_n \cdots \fermc_1 \fermc_i = 0\,.
\]
Similarly $g_0$ defines a morphism $(V,0) \lto (X,n)$. Let $f,g$ be the morphisms in $\cat{T}^\bullet$ corresponding to $f_0,g_0$ under the equivalence of Lemma \ref{lemma:equivcliffordthick}. To prove that $fg = 1_{(X,n)}$ and $gf = 1_{(V,0)}$ in $\cat{T}^{\bullet}$ it suffices to prove that $f_0 g_0 = 1^*_{(X,n)} = e_n$ and $g_0 f_0 = 1^*_{(V,0)}$ in $\cat{T}^{\star}$. But this is true by definition.
\end{proof}

@@

\begin{lemma} The $\nZ_2$-graded $k[x,z]$-module
\[
Y \l X = Y \otimes_{k[y]} J_V \otimes_{k[y]} X
\]
with the differential $d_Y \otimes 1 + 1 \otimes d_X$ is a finite rank matrix factorisation of $U - W$.
\end{lemma}
\begin{proof}
Since $V$ is a potential $J_V$ is a finite rank free $k$-module, and it follows that $Y \l X$ is a finite rank free $k[x,z]$-module.

\end{proof}
%If $\{ e_i \}_{i \in I}$ and $\{ f_j \}_{j \in J}$ are homogeneous bases of $Y, X$ over $k[z,y]$ and $k[y,x]$ respectively, and if $\{ v_k \}_{k \in K}$ is a $k$-basis for $J_V$ (which we give degree zero) then $\{ e_i \otimes v_k \otimes f_j \}_{i,j,k}$ is a $k[x,z]$-basis for $Y \l X$.

\begin{remark}\label{remark:inflation} If we choose a $k$-basis for $J_V$ then multiplication by $y_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[y_i]$ over $k$. The cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $y_i$ by the scalar matrix $[y_i]$. This ``inflation'' produces a matrix of polynomials over $k[x,z]$. 
\end{remark}

@@

By \cite[Appendix B]{dm1102.2957} there exists a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
\begin{equation}\label{eq:connection_nabla}
\nabla: \widehat{k[y]} \lto \widehat{k[y]} \otimes_{k[t]} \Omega^1_{k[t]/k}
\end{equation}
the components of which are $k$-linear operators $\partial_{t_i}: \widehat{k[y]} \lto \widehat{k[y]}$. A simple example of such a connection is given in Section \ref{example:computing_homs}. Using a chosen homogeneous basis $\{ e_a \otimes f_b \}_{a,b}$ for $Y \otimes X$ we may extend the operators $\partial_{t_i}$ extend to $k[x,z]$-linear operators
\begin{gather*}
\partial_{t_i}: Y \, \widehat{\otimes}\, X \lto Y \, \widehat{\otimes}\, X\\
e_a \otimes h(y) \otimes f_b \mapsto e_a \otimes \partial_{t_i}( h(y) ) \otimes f_b\,.
\end{gather*}

@@

\begin{definition}\label{defn:atiyah} The $i$th Atiyah class is this odd $k[x,z]$-linear operator
\[
\At^{Y,X}_i = [d_{Y \otimes X}, \partial_{t_i}]: Y \l X \lto Y \l X \,.
\]
Usually we just write $\At_i$ where it will not cause confusion.
\end{definition}

@@

\begin{lemma}\label{lemma:atiyahclosed} The operator $\At_i$ on $Y \l X$ is closed, and if $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations then there are $k[x,z]$-linear homotopies
\be\label{eq:atiyahclosednatural}
\At^{Y',X'}_i \circ \,( \psi \l \phi ) \simeq ( \psi \l \phi ) \circ \At^{Y,X}_i\,.
\ee
That is, the Atiyah classes are \emph{natural}.
\end{lemma}
\begin{proof}
The Atiyah class is closed since
\[
[d, \At_i] = [d, [d, \partial_{t_i}]] = 0\,.
\]
If $\kappa: Y \otimes X \lto Y' \otimes X'$ is any $k[x,y,z]$-linear even closed operator, 
\[
[ \kappa, [ d, \partial_{t_i} ] ] + [ \partial_{t_i}, [\kappa, d]] + [ d, [ \partial_{t_i}, \kappa] ] = 0
\]
from which we deduce that $[\partial_{t_i}, \kappa]$ is a homotopy establishing \eqref{eq:atiyahclosednatural}.
\end{proof}

@@

By the graded Jacobi identity
\begin{align*}
[\At_i, \At_j] &= [\At_i, [d, \partial_{t_j}]]\\
&= - [\partial_{t_j}, [\At_i, d]] - [d, [\partial_{t_j}, \At_i]]\\
&= [d, -[\partial_{t_j}, \At_i]]\,.
\end{align*}
Hence $[\ferm_i, \ferm_j] = [d, h_{ij}]$ where $h_{ij} = - [ \partial_{t_j}, \At_i ]$. Next we compute
\begin{align*}
[\partial_{y_i}(d_X), \At_j] &= [\partial_{y_i}(d_X), [d, \partial_{t_j}]]\\
&= -[\partial_{t_j}, [\partial_{y_i}(d_X), d]] + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\\
&= -[\partial_{t_j}, t_i] + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\\
&= -\delta_{ij} + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\,.
\end{align*}
Again we set $g_{ij} = [\partial_{t_j}, \partial_{y_i}(d_X)]$ for later use. We compute that
\begin{align*}
[ \fermc_i, \ferm_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \At_{q}, \At_j \big]\\
&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) [ \At_q, \At_j]\\
&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) [d, h_{qj}]\\
&= \delta_{ij} + \big[d, -g_{ij} - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) h_{qj}\big]\,.
\end{align*}
Finally, using Lemma \ref{lemma:commutator_of_lambdas}
\begin{align*}
[ \fermc_i, \fermc_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q}\partial_{y_j}(V) \At_{q} \Big]\\
&= [ \partial_{y_i}(d_X), \partial_{y_j}(d_X) ] + \frac{1}{2}\sum_q \partial_{y_q}\partial_{y_j}(V) \big[ \partial_{y_i}(d_X), \At_q \big]\\
&\quad + \frac{1}{2}\sum_q \partial_{y_q} \partial_{y_i}(V) \big[ \At_q, \partial_{y_j}(d_X) \big]\\
&\quad + \frac{1}{4}\sum_{p,q} \partial_{y_p} \partial_{y_i}(V) \partial_{y_q} \partial_{y_j}(V) \big[ \At_p, \At_q \big]\\
&= \partial_{y_iy_j}(V) + [d, - \partial_{y_j} \partial_{y_i}(d_X)]\\
&\qquad + \frac{1}{2}\sum_q \partial_{y_q} \partial_{y_j}(V) \left( -\delta_{iq} + [d, [ \partial_{t_q}, \partial_{y_i}(d_X)]] \right)\\
&\qquad + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \left( -\delta_{jq} + [d, [\partial_{t_q}, \partial_{y_j}(d_X)]] \right)\\
&\qquad + \frac{1}{4}\sum_{p,q} \partial_{y_p} \partial_{y_i}(V) \partial_{y_q} \partial_{y_j}(V) [d, -[\partial_{t_q}, \At_p]]\\
&= [d, c_{ij}]
\end{align*}
where
\begin{align*}
c_{ij} &= - \partial_{y_j} \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_j}(V)  [\partial_{t_q}, \partial_{y_i}(d_X)]\\
&\qquad + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) [\partial_{t_q}, \partial_{y_j}(d_X)]\\
&\qquad - \frac{1}{4} \sum_{p,q}  \partial_{y_p} \partial_{y_i}(V) \partial_{y_q} \partial_{y_j}(V)  [\partial_{t_q}, \At_p]\,.
\end{align*}
\end{proof}

@@

\begin{lemma}\label{lemma:associator} The morphism $\alpha: (Z \l Y) \l X \lto Z \l (Y \l X)$ is $C_m \otimes C_p$-linear.
\end{lemma}
\begin{proof}
We prove the $C_p$-linearity of $\alpha$, the proof for $C_m$ is similar. The algebra $C_p$ acts on the cut between $Z$ and $Y$ involving the variables $y_1,\ldots,y_p$. The action on $Z \l ( Y \l X ) = Z \otimes J_U \otimes (Y \otimes J_V \otimes X)$ is via $1 \otimes (\partial_{y_i}(d_Y) \otimes 1)$ and the Atiyah classes of 
\[
M = Z \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} \big( Y \otimes_{k[z]} J_V \otimes_{k[z]} X \big)
\]
relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$. Specifically, the generator $\ferm_i$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$. But this operator can be identified with an Atiyah class of the linear factorisation
\begin{equation}\label{eq:assoc_proof_M}
Z \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} \big( Y \otimes_{k[z]} \widehat{k[z]} \otimes_{k[z]} X \big)
\end{equation}
relative to the ring morphism
\begin{equation}\label{eq:assoc_proof_M2}
k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U, \partial_{z_1} V, \ldots, \partial_{z_m} V ]\,.
\end{equation}
By the same argument the action of $C_p$ on $(Z \l Y ) \l X$ is via $(1 \otimes \partial_{y_i}(d_Y)) \otimes 1$ and the Atiyah classes of $\big( Z \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} Y \big) \otimes_{k[z]} \widehat{k[z]} \otimes_{k[z]} X$ relative to the same ring morphism \eqref{eq:assoc_proof_M2}. It is therefore clear that the associator $\alpha$ identifies these two actions.
\end{proof}

@@

\begin{remark}\label{remark:relation_to_toby_paper} The cut operation presented here refines earlier work in \cite{dm1102.2957}. To see the connection, recall the idempotent $e_m \in C_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$. The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is 
\[
e_m' = \fermc_1 \cdots \fermc_m \ferm_m \cdots \ferm_1\,.
\]
Observe that each of the $\fermc_i$'s acts as $- \partial_{y_i}(d_X)$ because all of the $\ferm_j$'s to the right. Hence
\begin{align*}
e_m' &= (-1)^{\binom{m}{2}} \fermc_1 \cdots \fermc_m \ferm_1 \cdots \ferm_m \\
&= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
\end{align*}
which is precisely the idempotent which appears in \cite[Corollary 10.4]{dm1102.2957}.

@@

\begin{lemma} $\cat{T}(\theta_i^*) = \theta_i^*$.
\end{lemma}
\begin{proof}
Since $\theta_i^*$ commutes with $\delta$.
\end{proof}

>>>>

One of our motivations for introducing $\cat{C}$ is that it has an enrichment over affine schemes. This is not true of $\LG_k$, precisely because the composition is infinitary. We hope to return to this elsewhere, but for context we include a sketch assuming $k$ is an algebraically closed field of characteristic zero. Given potentials $W(x), V(y)$, a matrix factorisation of $V(y) - W(x)$ is after choosing a homogeneous basis just a matrix
\be\label{eq:intro_capitalD}
D \in M_{2r}( k[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (V(y) - W(x)) \cdot I_{2r}
\ee
where, dividing the matrix $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices. If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by an integer $s$, then we can easily parametrise matrix factorisations by the $k$-points of an affine scheme.

We may add further coordinates and equations to encode closed odd operators satisfying Clifford relations \eqref{eq:clifford_relations_intro} and, in this way, for a choice of parameters $\lambda = (r, s, \ldots)$ define a scheme $\mathscr{M}_{\lambda}(W,V)$ such that as sets
\begin{equation}\label{eq:param_frmf}
\operatorname{ob}(\cat{C}(W,V)) = \bigcup_{\lambda} \mathscr{M}_{\lambda}(W,V)_{k}
\end{equation}
where $Z_{k}$ denotes the $k$-points of a scheme $Z$. The cut operation is a polynomial function of its inputs, so there is an indexed family of morphisms of schemes
\be\label{eq:enrichment_morphisms_intro}
\mathscr{M}_\mu(V,U) \times \mathscr{M}_\lambda(W,V) \lto \mathscr{M}_{f(\lambda, \mu)}(W, U)
\ee
lifting the functor \eqref{eq:cut_functor_intro} on the level of objects for some function $f(\lambda, \mu)$ of indices. Finally, using the approach of Section \ref{example:computing_homs}, we can define for each pair of potentials $W,V$ and tuple of parameters $\lambda$ a vector bundle of Clifford representations
\be\label{eq:enrichment_intro_bundles}
\xymatrix{
\mathscr{H}\! om_{W,V,\lambda} \ar[d]\\
\mathscr{M}_\lambda(W,V) \times \mathscr{M}_\lambda(W,V)\,,
}
\ee
such that for matrix factorisations $X,X'$ of $V - W$ the fiber of this bundle over the point $(X',X)$ is the Clifford representation $(X')^{\vee} \l X$ of \eqref{eq:final_finite_model_hom}, which is isomorphic to the Hom-complex $\Hom_{k[x,y]}(X',X)$ tensored with a suitable spinor representation.

The enrichment of $\cat{C}$ then consists of the family of schemes $\mathscr{M}_\lambda(W,V)$, the composition morphisms \eqref{eq:enrichment_morphisms_intro}, the bundles \eqref{eq:enrichment_intro_bundles}, and various other data satisfying natural constraints which encode the structure of the bicategory.

@@

\begin{example} Small supercategories, superfunctors and supernatural transformations form a superbicategory $\Cat^{\operatorname{sup}}_k$.
\end{example}

@@

\begin{lemma}\label{lemma:whackamole} Let $X$ be a $C_n$-module in $\cat{T}$. The idempotent $e_n: X \lto X$ splits, say 
\[
\xymatrix@C+2pc{
X \ar@<1ex>[r]^-{f_0} & V \ar@<1ex>[l]^-{g_0}
}
\]
with $f_0 g_0 = 1_V$ and $g_0 f_0 = e_n$ and in $\cat{T}^\bullet$ there are mutually inverse isomorphisms
\[
\xymatrix@C+2pc{
(X, n) \ar@<1ex>[r]^-{f} & (V,0) \ar@<1ex>[l]^-{g}
}
\]
induced by $f_0,g_0$. In particular
\be
S_n^* \otimes_{C_n} X \cong V\,, \qquad S_n \otimes_k V \cong X\,.
\ee
\end{lemma}
\begin{proof}
The map $f_0$ is a morphism $(X,n) \lto (V,0)$ in $\cat{T}^{\star}$ since
\[
f_0 \fermc_i = f_0 e_n \fermc_i = f_0 \ferm_1 \cdots \ferm_n \fermc_n \cdots \fermc_1 \fermc_i = 0\,.
\]
Similarly $g_0$ is a morphism $(V,0) \lto (X,n)$ in $\cat{T}^{\star}$. Let $f,g$ be the morphisms in $\cat{T}^\bullet$ corresponding to $f_0,g_0$ under the equivalence of Lemma \ref{lemma:equivcliffordthick}. To prove that $fg = 1_{(X,n)}$ and $gf = 1_{(V,0)}$ in $\cat{T}^{\bullet}$ it suffices to prove that $g_0 f_0 = 1^*_{(X,n)} = e_n$ and $f_0 g_0 = 1^*_{(V,0)} = 1_V$ in $\cat{T}$. But this is true by definition.
\end{proof}

@@

\begin{lemma} The $\nZ_2$-graded $k[x,z]$-module
\[
Y \l X = Y \otimes_{k[y]} J_V \otimes_{k[y]} X
\]
with the differential $d_Y \otimes 1 + 1 \otimes d_X$ is a finite rank matrix factorisation of $U - W$.
\end{lemma}
\begin{proof}
Since $V$ is a potential $J_V$ is a finite rank free $k$-module, and it follows that $Y \l X$ is a finite rank free $k[x,z]$-module. 
\end{proof}
%If $\{ e_i \}_{i \in I}$ and $\{ f_j \}_{j \in J}$ are homogeneous bases of $Y, X$ over $k[z,y]$ and $k[y,x]$ respectively, and if $\{ v_k \}_{k \in K}$ is a $k$-basis for $J_V$ (which we give degree zero) then $\{ e_i \otimes v_k \otimes f_j \}_{i,j,k}$ is a $k[x,z]$-basis for $Y \l X$.

\begin{remark}\label{remark:inflation} If we choose a $k$-basis for $J_V$ then multiplication by $y_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[y_i]$ over $k$. The cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $y_i$ by the scalar matrix $[y_i]$ and $1 \in k$ by the identity matrix. This ``inflation'' produces a matrix of polynomials over $k[x,z]$. 
\end{remark}

@@

With $\Omega^1_{k[t]/k} \cong \bigoplus_{i=1}^m k[t] dt_i$ denoting K\"ahler diferentials, there exists by \cite[Appendix B]{dm1102.2957} a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
\begin{equation}\label{eq:connection_nabla}
\nabla: \widehat{k[y]} \lto \widehat{k[y]} \otimes_{k[t]} \Omega^1_{k[t]/k}
\end{equation}
the components of which are $k$-linear operators $\partial_{t_i}: \widehat{k[y]} \lto \widehat{k[y]}$. A simple example of such a connection is given in Section \ref{example:computing_homs}. Using a chosen homogeneous basis $\{ e_a \otimes f_b \}_{a,b}$ for $Y \otimes X$ we may extend the operators $\partial_{t_i}$ extend to $k[x,z]$-linear operators
\begin{gather*}
\partial_{t_i}: Y \, \widehat{\otimes}\, X \lto Y \, \widehat{\otimes}\, X\\
e_a \otimes h(y) \otimes f_b \mapsto e_a \otimes \partial_{t_i}( h(y) ) \otimes f_b\,.
\end{gather*}

@@

\begin{definition}\label{defn:atiyah} The $i$th Atiyah class is the odd $k[x,z]$-linear operator
\[
\At^{Y,X}_i = [d_{Y \otimes X}, \partial_{t_i}]: Y \l X \lto Y \l X \,.
\]
Usually we just write $\At_i$ where it will not cause confusion.
\end{definition}

@@

\begin{lemma}\label{lemma:atiyahclosed} $\At_i$ is $d_{Y \otimes X}$-closed, and if $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations then there are $k[x,z]$-linear homotopies
\be\label{eq:atiyahclosednatural}
\At^{Y',X'}_i \circ \,( \psi \l \phi ) \simeq ( \psi \l \phi ) \circ \At^{Y,X}_i\,.
\ee
That is, the Atiyah classes are \emph{natural}.
\end{lemma}
\begin{proof}
The Atiyah class is closed since (with $d = d_{Y \otimes X}$)
\[
[d, \At_i] = [d, [d, \partial_{t_i}]] = 0\,.
\]
If $\kappa: Y \otimes X \lto Y' \otimes X'$ is any $k[x,y,z]$-linear even closed operator, 
\[
[ \kappa, [ d, \partial_{t_i} ] ] + [ \partial_{t_i}, [\kappa, d]] + [ d, [ \partial_{t_i}, \kappa] ] = 0
\]
from which we deduce that $[\partial_{t_i}, \kappa]$ is a homotopy establishing \eqref{eq:atiyahclosednatural}.
\end{proof}

@@

With $d = d_{Y \otimes X}$ the differential on $Y \l X$, we have by the graded Jacobi identity
\begin{align*}
[\At_i, \At_j] &= [\At_i, [d, \partial_{t_j}]]\\
&= - [\partial_{t_j}, [\At_i, d]] - [d, [\partial_{t_j}, \At_i]]\\
&= [d, -[\partial_{t_j}, \At_i]]\,.
\end{align*}
Hence $[\ferm_i, \ferm_j] = [d, h_{ij}]$ where $h_{ij} = - [ \partial_{t_j}, \At_i ]$. Next we compute
\begin{align*}
[\partial_{y_i}(d_X), \At_j] &= [\partial_{y_i}(d_X), [d, \partial_{t_j}]]\\
&= -[\partial_{t_j}, [\partial_{y_i}(d_X), d]] + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\\
&= -[\partial_{t_j}, t_i] + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\\
&= -\delta_{ij} + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\,.
\end{align*}
Again we set $g_{ij} = [\partial_{t_j}, \partial_{y_i}(d_X)]$ for later use. We compute that
\begin{align*}
[ \fermc_i, \ferm_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \At_{q}, \At_j \big]\\
&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) [ \At_q, \At_j]\\
&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) [d, h_{qj}]\\
&= \delta_{ij} + \big[d, -g_{ij} - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) h_{qj}\big]\,.
\end{align*}
Finally, using Lemma \ref{lemma:commutator_of_lambdas}
\begin{align*}
[ \fermc_i, \fermc_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q}\partial_{y_j}(V) \At_{q} \Big]\\
&= [ \partial_{y_i}(d_X), \partial_{y_j}(d_X) ] + \frac{1}{2}\sum_q \partial_{y_q}\partial_{y_j}(V) \big[ \partial_{y_i}(d_X), \At_q \big]\\
&\quad + \frac{1}{2}\sum_q \partial_{y_q} \partial_{y_i}(V) \big[ \At_q, \partial_{y_j}(d_X) \big]\\
&\quad + \frac{1}{4}\sum_{p,q} \partial_{y_p} \partial_{y_i}(V) \partial_{y_q} \partial_{y_j}(V) \big[ \At_p, \At_q \big]\\
&= \partial_{y_iy_j}(V) + [d, - \partial_{y_j} \partial_{y_i}(d_X)]\\
&\qquad + \frac{1}{2}\sum_q \partial_{y_q} \partial_{y_j}(V) \left( -\delta_{iq} + [d, [ \partial_{t_q}, \partial_{y_i}(d_X)]] \right)\\
&\qquad + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \left( -\delta_{jq} + [d, [\partial_{t_q}, \partial_{y_j}(d_X)]] \right)\\
&\qquad + \frac{1}{4}\sum_{p,q} \partial_{y_p} \partial_{y_i}(V) \partial_{y_q} \partial_{y_j}(V) [d, -[\partial_{t_q}, \At_p]]\\
&= [d, c_{ij}]
\end{align*}
where
\begin{align*}
c_{ij} &= - \partial_{y_j} \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_j}(V)  [\partial_{t_q}, \partial_{y_i}(d_X)]\\
&\qquad + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) [\partial_{t_q}, \partial_{y_j}(d_X)]\\
&\qquad - \frac{1}{4} \sum_{p,q}  \partial_{y_p} \partial_{y_i}(V) \partial_{y_q} \partial_{y_j}(V)  [\partial_{t_q}, \At_p]\,.
\end{align*}
\end{proof}

@@

\begin{lemma}\label{lemma:associator} The morphism $\alpha: (Z \l Y) \l X \lto Z \l (Y \l X)$ is $C_m \otimes C_p$-linear.
\end{lemma}
\begin{proof}
We prove the $C_p$-linearity of $\alpha$, the proof for $C_m$ is similar. The algebra $C_p$ acts on the cut between $Z$ and $Y$ involving the variables $y_1,\ldots,y_p$. The action on $Z \l ( Y \l X ) = Z \otimes J_U \otimes (Y \otimes J_V \otimes X)$ is via $1 \otimes (\partial_{y_i}(d_Y) \otimes 1)$ and the Atiyah classes of 
\[
M = Z \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} \big( Y \otimes_{k[z]} J_V \otimes_{k[z]} X \big)
\]
relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$. Specifically, the generator $\ferm_i$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$. But this operator can be identified with an Atiyah class of
\begin{equation}\label{eq:assoc_proof_M}
Z \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} \big( Y \otimes_{k[z]} \widehat{k[z]} \otimes_{k[z]} X \big)
\end{equation}
relative to the ring morphism
\begin{equation}\label{eq:assoc_proof_M2}
k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U, \partial_{z_1} V, \ldots, \partial_{z_m} V ]\,.
\end{equation}
By the same argument the action of $C_p$ on $(Z \l Y ) \l X$ is via $(1 \otimes \partial_{y_i}(d_Y)) \otimes 1$ and the Atiyah classes of $\big( Z \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} Y \big) \otimes_{k[z]} \widehat{k[z]} \otimes_{k[z]} X$ relative to the same ring morphism \eqref{eq:assoc_proof_M2}. It is therefore clear that the associator $\alpha$ identifies these two actions.
\end{proof}

@@

\begin{remark}\label{remark:relation_to_toby_paper} The cut operation presented here refines earlier work in \cite{dm1102.2957}. To see the connection, recall the idempotent $e_m \in C_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto $k \cdot 1 \subset S_m$. The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is 
\[
e_m' = \fermc_1 \cdots \fermc_m \ferm_m \cdots \ferm_1\,.
\]
Observe that each of the $\fermc_i$'s acts as $- \partial_{y_i}(d_X)$ because all of the $\ferm_j$'s to the right. Hence
\begin{align*}
e_m' &= (-1)^{\binom{m}{2}} \fermc_1 \cdots \fermc_m \ferm_1 \cdots \ferm_m \\
&= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
\end{align*}
which is precisely the idempotent which appears in \cite[Corollary 10.4]{dm1102.2957}.

@@

\begin{lemma} $\cat{T}(\theta_i^*) = \theta_i^*$.
\end{lemma}
\begin{proof}
Since $\theta_i^*$ anticommutes with $\delta$.
\end{proof}
